\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-04 coq-example.tex
Fix statistics

Our formulation for bare STLC is around 400+ LOCs; the two families implementing product and boolean features both take around 300+ LOCs. 
% need comparison with the original implementation

The biggest difference in the proof script comes from the fact that we
are handling ``extensible'' inductive types instead of real inductive
types, and thus the inversion tactic is not working and we have to manually
create inversion lemmas. This leads to a mild code bloat.

Another difference comes from the fact that we need to use "Closing
Fact" to manually verify the computational rules for each recursor and
use tactics to ``run'' the recursor by repeatedly "rewrite" using those
verified computational rules. This part is possible to be automatically
generated by the plugin, but still it will require propositional
computational rules.

>>>>

Our formulation for bare STLC is around 400+ LOCs; the two families implementing product and boolean features both take around 250+ LOCs. 
% need comparison with the original implementation

The biggest difference in the proof script comes from the fact that we
are handling ``extensible'' inductive types instead of real inductive
types, and thus the inversion tactic is not working and we have to manually
create inversion lemmas.

Another difference comes from the fact that we need to use "Closing
Fact" to manually verify the computational rules for each recursor and
use tactics to ``run'' the recursor by repeatedly "rewrite" using those
verified computational rules. This part is possible to be automatically
generated by the plugin, but still it will require propositional 
computational rules.  What's more, we don't yet support the \mintinline{Coq}{Hint}. These three differences on experience lead to a mild code bloat.
